Token-level author diarization using clustering of stylistic contexts

### 2017-06-03 paper/paper.tex
Final push before moving the repository

For further work, it would be good to search for more useful basic features, make a deeper examination of the feature transformation, try other clustering algorithms and use more systematic approach for choosing hyperparameters. It would be also interesting to try the trainable feature transformation approach on other authorship analysis problems.

>>>>

For further work, it would be good to search for more useful basic features, make a deeper examination of the feature transformation, try other clustering algorithms and a use more systematic approach for choosing hyperparameters. It would be also interesting to try the trainable feature transformation approach on other authorship analysis problems.
